---
title: "Results"
author: "Laura Tiemann"
output:
  html_document:
    toc: yes
    theme: flatly
    highlight: haddock
    code_download: yes
    df_print: paged
---

Display of results, consisting in descriptive results, the mediation analysis, and an explorative analysis resulting of a correlation matrix.

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(mediation)
library(corrplot)
library(mltools)
library(ggcorrplot)
library(data.table)
```

# Loading the Prepared and Preprocessed Data

```{r}

data <- read.csv("bachelor_thesis_prepared_data.csv") 


data_preprocessed <- read.csv("bachelor_thesis_preprocessed_data.csv") 

```


# Demographic Data

## Age 
```{r}
data_age_mean <- na.omit(data$Age) %>% 
  mean() 

data_age_sd <- na.omit(data$Age) %>% 
  sd() 

data_age_mean
data_age_sd

```

## Gender 
```{r}
data_gender <- data_preprocessed %>% 
  dplyr::select(Gender) %>%
  group_by(Gender) %>% 
  dplyr::count(Gender) %>% 
  summarise(Anteil = round(100*n / sum(.$n), digits = 2)) %>% 
  mutate(Gender = case_when(
    Gender == "d" ~ "Diverse",
    Gender == "m" ~ "Male",
    Gender == "f" ~ "Female"
  )) %>% 
  dplyr::arrange(desc(Anteil))
  
data_gender
```

## Education 
```{r}
data_education <- data_preprocessed %>% 
  dplyr::select(Education) %>%
  group_by(Education) %>% 
  dplyr::count(Education) %>% 
  summarise(Anteil = round(100*n / sum(.$n), digits = 2)) %>% 
  dplyr::arrange(desc(Anteil)) 

data_education
```


# Descriptive Results 

## Journaling, Counterfactuals, and Self-efficacy
```{r}
descriptive_results <- data_preprocessed %>% 
  dplyr::select(Journaling, Counterfactuals, SelfEfficacy) %>% 
  summary()

descriptive_results

```


## Descriminating Journaling 

### Frequency

```{r}


data_journal <- data %>% 
  dplyr::select(Journaling1) %>% 
  
  group_by(Journaling1) %>% 
  dplyr::count(Journaling1) %>% 
  summarise(Anteil = round(100*n / sum(.$n), digits = 2)) %>% 
  mutate(Journaling1 = case_when(
    Journaling1 == 1 ~ "Never",
    Journaling1 == 2 ~ "Seldom",
    Journaling1 == 3 ~ "Sometimes",
    Journaling1 == 4 ~ "Often",
    Journaling1 == 5 ~ "Very often",

    TRUE ~ as.character(Journaling1)  # Default case, no change
  ))  %>% 
  rename(Journaling_Häufigkeit = "Journaling1") %>% 
  dplyr::arrange(desc(Anteil))

data_journal


```


### Last Entry

```{r}


data_journal3 <- data %>% 
  dplyr::select(Journaling3) %>% 
  
  group_by(Journaling3) %>% 
  dplyr::count(Journaling3) %>% 
  summarise(Anteil = round(100*n / sum(.$n), digits = 2)) %>% 
  mutate(Journaling3 = case_when(
    Journaling3 == 1 ~ "Never",
    Journaling3 == 2 ~ "More than a month ago",
    Journaling3 == 3 ~ "This month",
    Journaling3 == 4 ~ "This week",
    Journaling3 == 5 ~ "Today",

    TRUE ~ as.character(Journaling3)  # Default case, no change
  ))  %>% 
  rename(Journaling_last_entry = "Journaling3") %>% 
  dplyr::arrange(desc(Anteil))

data_journal3


```


# Mediation Analysis 

## Creating the Regression Models

### Counterfactual Thinking and Journaling 

```{r}
path_a <- lm(Counterfactuals ~ Journaling, data_preprocessed)
summary(path_a)
```

### Self-efficacy Through Journaling and Counterfactual Thinking  

```{r}
path_bc <- lm(SelfEfficacy ~ Journaling + Counterfactuals, data_preprocessed)
summary(path_bc)
```


## Analysis

```{r}
results <- mediate(path_a, path_bc, treat = "Journaling", mediator = "Counterfactuals", boot = TRUE, sims = 2000)

summary(results)

```



# Explorative Results 

## Correlation Matrix 


### Preparing the Data 

#### Factorization
```{r}
data_preprocessed$Gender <- as.factor(data_preprocessed$Gender)
data_preprocessed$Education <- as.factor(data_preprocessed$Education)
```

#### One-hot Encoding 
```{r}
data_encoded <- one_hot(as.data.table(data_preprocessed))

```
#### Correlation

```{r}
correlation_matrix <- cor(data_encoded, use = "pairwise.complete.obs")

```


### Plotting the Matrix 

```{r, warning=FALSE}
correlation_matrix %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=3, tl.cex = 10) + 
      theme(plot.title = element_text(size = 20), 
            plot.subtitle = element_text(size = 15), 
            plot.caption = element_text(size = 12)) +
      coord_fixed(ratio = 1) 

```

## Age and Self-Efficacy 

```{r}
model_age_se <- lm(SelfEfficacy ~ Age, data = data_preprocessed)

summary(model_age_se)

```


## Gender


### Gender and Journaling

```{r}
model_journaling_gender <- glm(data_preprocessed$Journaling ~ data_preprocessed$Gender, data = data_preprocessed)


summary(model_journaling_gender)

```

### Gender and Counterfactual Thinking 

```{r}
model_cft_gender <- glm(data_preprocessed$Counterfactuals ~ data_preprocessed$Gender, data = data_preprocessed)


cft_gender <- summary(model_cft_gender)

```



### Gender and Self-Efficacy 

```{r}
model_se_gender <- glm(data_preprocessed$SelfEfficacy ~ data_preprocessed$Gender, data = data_preprocessed)


summary(model_se_gender)
```



## Journaling Frequency 

### Frequency

```{r}
model_frequency <- lm(SelfEfficacy ~ Journaling3, data = data)


summary(model_frequency)
```


### Last Entry

```{r}

model_LastEntry <- lm(SelfEfficacy ~ Journaling1, data = data)


summary(model_LastEntry)

```









