---
title: "Preprocessing"
author: "Laura Tiemann"
output:
  html_document:
    toc: yes
    theme: flatly
    highlight: haddock
    code_download: yes
    df_print: paged
---

Preprocessing of the survey data, including renaming variables, calculating the individual scores for the scales, and testing for the assumptions of linear regression.


```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(car)
library(lmtest)
library(nortest)
```

# Loading the Data
For the sake of providing anonymity to the participants of the study, the data in the Git-repository does not include the raw data and rather the prepared data that already includes the individual summation of the scales. 
Hence, the following steps can be skipped when replicating the statistical analysis.

```{r}
data <- read.csv("results_bachelorthesis.csv") %>% 
  dplyr::select(-Ereignissimulation, -Verlosung, -Journaling2) %>% 
  rename(Gender = "ï..Geschlecht") %>% 
  rename(Age = "Alter") %>% 
  rename(Education = "Bildungsstand") 

head(data)

```
# Preprocessing

## Changing Names of Values {.tabset}

### Education 

```{r}
data <- data %>% 
  mutate(Education = case_when(
    Education == "Abi" ~ "Alevels",
    Education == "AS" ~ "University",
    Education == "Real" ~ "Realschule",
    Education == "Haupt" ~ "Hauptschule",
  )) 

head(data)

```

### Gender

```{r}
data <- data %>% 
    mutate(Gender = case_when(
    Gender == "kA" ~ NA,
    Gender == "m" ~ "m",
    Gender == "w" ~ "f",
    Gender == "d" ~ "d"
  ))

head(data)
```

## Calculating the Individual Scores

Calculating the individual scores for the scales of Journaling, Counterfactual Thinking, and Self-efficacy. 

```{r}
journaling_columns <- grep("Journaling", names(data), value = TRUE)
counterfactual_columns <- grep("Counterfactuals", names(data), value = TRUE)
selfefficacy_columns <- grep("Selbstwirksamkeit", names(data), value = TRUE)

data$Journaling <- rowSums(data[c(journaling_columns)]) 
data$Counterfactuals <- rowSums(data[c(counterfactual_columns)]) 
data$SelfEfficacy <- rowSums(data[c(selfefficacy_columns)]) 


```


## Selection of Important Columns
```{r}
data_preprocessed <- data %>% 
  dplyr::select(Age, Gender, Education, Journaling, Counterfactuals, SelfEfficacy)

head(data_preprocessed)

```

# Assumptions of Linear Regression 

For the later performed mediation analysis that receives two regression models as input, the assumptions of linear regression need to be tested. 

## Creating the Regression Models {.tabset}

### Counterfactual Thinking and Journaling 

```{r}
path_a <- lm(Counterfactuals ~ Journaling, data_preprocessed)

```

### Self-efficacy Through Journaling and Counterfactual Thinking  

```{r}
path_bc <- lm(SelfEfficacy ~ Journaling + Counterfactuals, data_preprocessed)

```


## Linear Relationship {.tabset}

Linear relationship is tested by using the Pearson correlation which is bound between -1 and 1. 1 indicates a strong positive correlation, while -1 indicates a strong negative correlation. Values around 0 indicate no correlation.

### Counterfactual Thinking ~ Journaling 

```{r}
cor(data_preprocessed$Counterfactuals, data_preprocessed$Journaling, use='complete.obs', method = "pearson")
```


### Self-efficacy ~ Journaling + Counterfactual Thinking

```{r}
cor(data_preprocessed$SelfEfficacy, data_preprocessed$Journaling + data_preprocessed$Counterfactuals, use='complete.obs', method = "pearson")
```


## Independence {.tabset}

Independence is tested by employing the Durbin-Watson-Test.

### Counterfactual Thinking ~ Journaling 
```{r}
durbinWatsonTest(path_a)
```


### Self-efficacy ~ Journaling + Counterfactual Thinking
```{r}
durbinWatsonTest(path_bc)
```

## Homoscedasticity {.tabset}

Homoscedasticity is tested by using the Goldfeld-Quandt test.

### Counterfactual Thinking ~ Journaling 

```{r}
gqtest(path_a)
```

### Self-efficacy ~ Journaling + Counterfactual Thinking

```{r}
gqtest(path_bc)
```

## Normality {.tabset}

Normality is tested with the Anderson-Darling-Test. 

### Journaling 
```{r}
ad.test(data_preprocessed$Journaling)
```



### Counterfactual Thinking
```{r}
ad.test(data_preprocessed$Counterfactuals)
```


### Self-efficacy

```{r}
ad.test(data_preprocessed$SelfEfficacy)
```







